---
title: "Community Flammability Graham"
author: "Jennifer Pannell"
date: "13/09/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
library(tidyverse)
library(reshape2)
library(ggbiplot)
library(FD)
library(gridExtra)
```
#Intro
This R markdown will calculate individual species flammability values, and then merge that with the community cover abundance data.
It takes as input the following files:
burndat.csv (cleaned burn data from amalgamated from files sent by Tim Curran & team)
Plot_IV.csv (plot level species Importance Values - output of cover_summaries.Rmd)
CurrentNVSNames.csv (NVS codes and associated species names downloaded from Landcare)
traits_all.csv (cleaned plant trait data collated by Jen from Ecotraits and other online sources e.g. NZ Flora)

Output is community_flam.csv - plot-level community flammability scores with associated vegetation type, to feed into landscape.Rmd

##Notes on data cleaning pre-reading into R
*I amalgamated all data from Tim's group - different spreadsheets
*Ignition time all seemed to be pre-inversion (i.e. shows actual time not inverse like Padulles et al paper)
*Discrepancies between how non burning samples recorded for ignition time (temp = 150, others = 0) - I have assigned these times of 11s to distinguish them from ones that did burn (max = 10)
*Data from Xinglei has missing values (#DIV/0!) for a number of ignition time scores. Not sure why, no formulae in spreadsheet.
*Update - because his data are means, of the one Azhar sent, and he hasn't removed zeroes etc. Have replaced with NA
*Data from Azhar has some inconsistency too, measured by different people? Some species names don't match NVS, some have no times recorded, some that seem to be no burns have been given inconsistent ignite times of 11, 1, 0.5 or 0, some have been given temps of 0 which I think also are no burns (have assigned them 11 150 0 0 like all others)

# Read in data
```{r read species burn data, echo=T, results='hide'}
burn<-read.csv("../data/burndat.csv", header=T, stringsAsFactors = F)
# Make sure NVS code is all caps
# Strip white space (also from Species Name)
burn$NVSCode<-burn$NVSCode%>%toupper()%>%tm::stripWhitespace()%>%trimws(.,"both")
burn$SpeciesName<-burn$SpeciesName%>%tm::stripWhitespace()%>%trimws(.,"both")
# make sure data is write structure
burn$IgnitionTime<-as.numeric(burn$IgnitionTime)
```

Fix missing ignition times
```{r deal with missing ignition time data}
# assume it can be predicted by other 3 vars as they are all quite correlated
# use negative binomial to account for the overdispersion and disallow negative values
mod<-MASS::glm.nb(as.integer(IgnitionTime)~BurnBiomass+MaxTemp+BurnTime, data=burn)

# predict ignition time where missing based on other 3 values and nb model
for(i in 1:nrow(burn)){
  if (is.na(burn$IgnitionTime[i])==TRUE){
    burn$IgnitionTime[i]<-predict(mod, newdata=burn[i,], type="response")
  }
}

# inversely rescale ignitability so it's higher for sp that are more flammable
burn$Ignitability<-max(burn$IgnitionTime)-burn$IgnitionTime

rm(mod, i)
```

# Create community matrix
# Just using canterbury farm at the mo as it's the only farm with a landscape
# But keeping rest of the analysis (pca etc) the same as community.Rmd - based on data from all 3 farms. 
```{r read in community data}
community<-read.csv2("../data/Plot_IV.csv", header=T, sep=",",  stringsAsFactors = F)
community$SpeciesName<-community$SpeciesName%>%toupper()%>%tm::stripWhitespace()%>%trimws(.,"both")
community$PlotID<-community$PlotID%>%toupper()%>%tm::stripWhitespace()%>%trimws(.,"both")
names(community)[2]<-"NVSCode" #rename this to be consistent with burn
community$IV<-as.numeric(community$IV)

# create matrix with plots in rows, species in columns, IV as values
cmat<-dcast(community, formula=PlotID~NVSCode, value.var = "IV", sum)

# add full latin name to community dataframe
nvs<-read.csv("../data/CurrentNVSNames.csv", header=T, sep=",", stringsAsFactors = F)
nvs$NVSCode<-nvs$NVSCode%>%toupper()%>%tm::stripWhitespace()%>%trimws(.,"both")
community<-merge(community, nvs[,c(1,13)], by="NVSCode")
names(community)[15]<-"SpeciesName"
community$SpeciesName<-community$SpeciesName%>%tm::stripWhitespace()%>%trimws(.,"both")
```

# Identify species with no flammability data and assign them mean value for genus or closest in terms of traits
```{r deal with missing species, echo=T, results='hide'}
# do we have flam data for all spp?
community$flamdata<-community$NVSCode%in%burn$NVSCode

# what about data for same genus
burn$Genus<-stringr::word(burn$SpeciesName, 1)
community$Genus<-stringr::word(community$SpeciesName, 1)
community$genusflam<-community$Genus%in%burn$Genus

# select species that have no flam data but have a matching genus
flamgen<- subset(community, flamdata==FALSE&genusflam==TRUE)

# create empty data frame
SpeciesName<-unique(flamgen$SpeciesName)
Sample<-rep(NA, length(SpeciesName))
NVSCode<-unique(flamgen$NVSCode)
IgnitionTime<-rep(NA, length(SpeciesName))
MaxTemp<-rep(NA, length(SpeciesName))
BurnTime<-rep(NA, length(SpeciesName))
BurnBiomass<-rep(NA, length(SpeciesName))
Ignitability<-rep(NA, length(SpeciesName))

newdat<-data.frame(SpeciesName, Sample, NVSCode, IgnitionTime, MaxTemp, BurnTime, BurnBiomass, Ignitability)
newdat$Genus<-stringr::word(newdat$SpeciesName, 1)

# apply genus mean to each species in newdat
for (i in 1:nrow(newdat)){
  a<-newdat$Genus[i]
  genusmeans<-burn %>%
    group_by(Genus) %>%
    summarise_at(c("IgnitionTime", "MaxTemp", "BurnTime", "BurnBiomass", "Ignitability"), mean, na.rm=TRUE)%>%
    subset(Genus==a)
  newdat[i,c(4:8)]<-genusmeans[1,2:6]
  rm(a, genusmeans)
}

burn<-rbind(burn, newdat)

rm(newdat,i,BurnBiomass, BurnTime, Ignitability, IgnitionTime, MaxTemp, NVSCode, Sample, SpeciesName, flamgen)

```

```{r other missing species based on expert opinion}
## following discussions with Tim Curran, he thinks best parallel for nikau palm (which has no congeners in burn dataset, nor similar species trait-wise) would be either cabbage tree or tree ferns. Suggestion is to run with both and see what difference it makes to overall result, then choose one. 

# note that this does not apply in canterbury as there is no nikau in canterbury. 

# 1. assign nikau palm value for cabbage tree
  cabbage<-burn[burn$NVSCode=="CORAUS",]%>%
    summarise_at(c("IgnitionTime", "MaxTemp", "BurnTime", "BurnBiomass", "Ignitability"), mean, na.rm=TRUE)%>%
    cbind(NVSCode="RHOSAP",.)%>%
    cbind(Sample="NA",.)%>%
    cbind(SpeciesName="Rhopalostylis sapida",.)%>%
    cbind(.,Genus="Rhopalostylis")
 #  
  burn<-rbind(burn, cabbage)
  rm(cabbage)
# # also update the community data to say we do have burn data for nikau 
  community <- within(community, flamdata[NVSCode == "RHOSAP" & flamdata=="FALSE"] <- "TRUE")

 # 2. Re-run this code and remove below comments, comment out 1 instead, run with mean of tree ferns instead - what's the difference in flammability values for the veg types?
 
 #   treefern<-burn[burn$NVSCode=="DICSQU"|burn$NVSCode=="CYAMED"|burn$NVSCode=="CYADEA",]%>%
 #     summarise_at(c("IgnitionTime", "MaxTemp", "BurnTime", "BurnBiomass", "Ignitability"), mean, na.rm=TRUE)%>%
 #     cbind(NVSCode="RHOSAP",.)%>%
 #     cbind(Sample="NA",.)%>%
 #     cbind(SpeciesName="Rhopalostylis sapida",.)%>%
 #     cbind(.,Genus="Rhopalostylis")
 # #  
 #   burn<-rbind(burn, treefern)
 #   rm(treefern)
 # #also update the community data to say we do have burn data for nikau 
 #  community <- within(community, flamdata[NVSCode == "RHOSAP" & flamdata=="FALSE"] <- "TRUE")

```

```{r traits PCA}
## read in trait data and merge with burn
traits<-read.csv("../data/traits_all.csv", header=T, na.strings="", stringsAsFactors = F)
names(traits)[1]<-"SpeciesName"
traits$SpeciesName<-traits$SpeciesName%>%tm::stripWhitespace()%>%trimws(.,"both")

## do some simplification of trait data - vegetative organs and leaf form
for(i in 1:length(traits$Vegetative.Organs)){
  if (traits$Vegetative.Organs[i]!="None"){
    traits$Vegetative.Organs[i]<-"Yes"
  }
}

# finds leaf forms containing words grass, needle leaved, e.g. "needle leaved -2  needles" and just simplify to grass # & needle. If not grass, needle or broad just call it "other"
for(i in 1:length(traits$Leaf.Form)){
  if(isTRUE(startsWith(traits$Leaf.Form[i], "Grass"))) {
    traits$Leaf.Form[i]<-"Grass-leaved"
  }else if(isTRUE(startsWith(traits$Leaf.Form[i], "Needle"))){
    traits$Leaf.Form[i]<-"Needle-leaved"
  }else if(isFALSE(startsWith(traits$Leaf.Form[i],"Broad"))){
    traits$Leaf.Form[i]<-"Other"
  }
}

# create dataset with all burn samples and trait data
traits2<-merge(traits, burn, by="SpeciesName")

# do some exploratory analyses
# histograms show that nearly all the variables are extremely skewed, which is the reason the pca is so uninformative
# plotted log histograms to see whether log-tranformation fixes this (it does)
traits2$logheight<-log(traits2$Max.Mean.Height..m.+1)
traits2$logleaflength<-log(traits2$Max.Mean.Leaf.Length..mm.+1)
traits2$logleafwidth<-log(traits2$Leaf.Width..mm.+1)
traits2$logleafarea<-log(traits2$LeafArea+1)
traits2$logburntime<-log(traits2$BurnTime+1)
traits2$logburnbio<-log(traits2$BurnBiomass+1)

## do a pca with the burn & trait data
## drop area bc it's highly cor'd with both width & length (which are not that cor'd)
## get rid of non-numeric vars
pca_dat1<-traits2[,c(24,27,29:31,33:34)]%>%aggregate(by=list(traits2$SpeciesName), FUN=mean, na.rm=T)
names(pca_dat1)[1]<-"SpeciesName"
pca_dat1<-merge(traits, pca_dat1, by="SpeciesName", all.x=F)
colnames(pca_dat1)[21:27]<-c("Combustibility","Ignitability","Height", 
                             "Leaf length", "Leaf width",
                             "Sustainability", "Consumability")
labs<-colnames(pca_dat1)[21:27]
traits.pca <- prcomp(pca_dat1[,c(21:27)], scale = TRUE) # perform a principal components analysis
summary(traits.pca)   # look at the variance explained
ggscreeplot(traits.pca) # scree plot

# plot pca biplot with groupings of diff categorical traits
plot1<-ggbiplot(traits.pca, groups = pca_dat1$Raunkiaer.Life.Mode, ellipse = TRUE)
# main plot for report
source("jen_ggbiplot.R") # load custom ggbiplot function
plot2<-jen.ggbiplot(traits.pca, groups = pca_dat1$Regeneration, ellipse = TRUE, obs.scale = 2, var.scale=1,
                    labels.size = 5)
# make the labels for the plots
pca_dat1$Regeneration<-as.factor(pca_dat1$Regeneration)

# other var plots
plot3<-ggbiplot(traits.pca, groups = pca_dat1$Shade.Tolerance, ellipse = TRUE, obs.scale = 1.5, var.scale=1)
plot4<-ggbiplot(traits.pca, groups = pca_dat1$Spines.or.Burrs, ellipse = TRUE)
plot5<-ggbiplot(traits.pca, groups = pca_dat1$Vegetative.Organs, ellipse = TRUE)
plot6<-ggbiplot(traits.pca, groups = pca_dat1$Leaf.Form, ellipse = TRUE)
plot7<-ggbiplot(traits.pca, groups = pca_dat1$Leaf.Longevity, ellipse = TRUE)
plot8<-ggbiplot(traits.pca, groups = pca_dat1$Origin, ellipse = TRUE)
plot9<-ggbiplot(traits.pca, groups = pca_dat1$Native, ellipse = TRUE)
plot10<-ggbiplot(traits.pca, groups = pca_dat1$Woody, ellipse = TRUE)
plot11<-ggbiplot(traits.pca, groups = pca_dat1$Type, ellipse = TRUE)
plot12<-ggbiplot(traits.pca, groups = pca_dat1$LeafType, ellipse = TRUE)
plot13<-ggbiplot(traits.pca, groups = pca_dat1$LeafMargin, ellipse = TRUE)
plot14<-ggbiplot(traits.pca, groups = pca_dat1$Simple, ellipse = TRUE)

# saves the plots - commented out to avoid re-saving them - remove # if want to redo them

#ggsave("../results/lifemode_pca.png", plot=plot1, width=8, height=8, units=c("in"),dpi=300 )
#ggsave("../results/regen_pca.png", plot=plot2, width=8, height=8, units=c("in"),dpi=300 )
#ggsave("../results/shade_pca.png", plot=plot3, width=8, height=8, units=c("in"),dpi=300 )
#ggsave("../results/spines_pca.png", plot=plot4, width=8, height=8, units=c("in"),dpi=300 )
#ggsave("../results/vegetative_pca.png", plot=plot5, width=8, height=8, units=c("in"),dpi=300 )
#ggsave("../results/leafform_pca.png", plot=plot6, width=8, height=8, units=c("in"),dpi=300 )
#ggsave("../results/leaflongevity_pca.png", plot=plot7, width=8, height=8, units=c("in"),dpi=300 )
#ggsave("../results/origin_pca.png", plot=plot8, width=8, height=8, units=c("in"),dpi=300 )
#ggsave("../results/native_pca.png", plot=plot9, width=8, height=8, units=c("in"),dpi=300 )
#ggsave("../results/woody_pca.png", plot=plot10, width=8, height=8, units=c("in"),dpi=300 )
#ggsave("../results/type_pca.png", plot=plot11, width=8, height=8, units=c("in"),dpi=300 )
#ggsave("../results/leaftype_pca.png", plot=plot12, width=8, height=8, units=c("in"),dpi=300 )
#ggsave("../results/leafmargin_pca.png", plot=plot13, width=8, height=8, units=c("in"),dpi=300 )
#ggsave("../results/simple_pca.png", plot=plot14, width=8, height=8, units=c("in"),dpi=300 )

rm(plot1, plot3, plot4, plot5, plot6, plot7, plot8, plot9, plot10, plot11, plot12, plot13, plot14)

```

```{r use traits to estimate missing burn data}
# get all species from community data that still have no burn data or matching genus
SpeciesName<- subset(community, flamdata==FALSE&genusflam==FALSE)%>%.[,15]%>%unique()
# build glms based on contin vars and add each factor at a time. 
# based on pca plots and which ones have sensible ecological reasons plus not too many levels 

# burnt biomass should be a logistic regression as is % data - do this on the raw data
summary(bb.mod<-glm(cbind(round(BurnBiomass),round(100-BurnBiomass))~
                      logheight+logleaflength+logleafwidth+Regeneration+
                      Shade.Tolerance+Leaf.Form+Leaf.Longevity+Native+Type+Woody+Simple,
                    data=traits2,family=binomial))

# model diagnostics
anova(bb.mod, test="LRT")
plot(bb.mod)
DescTools::PseudoR2(bb.mod)#0.19 mcfadden - that's not bad
# predict for non burned spp
# first need to do the log numeric vars for traits data frame too
traits$logheight<-log(traits$Max.Mean.Height..m.+1)
traits$logleaflength<-log(traits$Max.Mean.Leaf.Length..mm.+1)
traits$logleafwidth<-log(traits$Leaf.Width..mm.+1)
traits$logleafarea<-log(traits$LeafArea+1)

# which ones were missing burn data? create data frame for prediction
traits$missing<-traits$SpeciesName%in%SpeciesName
missing_burn<-subset(traits, missing=="TRUE")

missing_burn$BurnBiomass<-predict.glm(bb.mod, type="response", newdata=missing_burn)*100

# now for burn time
# model as negative binomial, again use the raw
# but it's also very 0 inflated and ordinary nb are terrible. try zinb.
# fitted with full vars as the biomass then dropped non significant - woody, native,regeneration,height
summary(bt.mod<-pscl::zeroinfl(round(BurnTime)~
                         logleaflength+logleafwidth+Shade.Tolerance+Leaf.Form+Leaf.Longevity+Type+Simple|
                        logheight+logleafwidth+Shade.Tolerance+Leaf.Form+Leaf.Longevity+Type,
                       data = traits2, dist = "negbin", EM = TRUE))
# model diagnostics
car::Anova(bt.mod)
# get the predicted values so can do some diagnostic plots (not coded here)
traits2$pred_bt<-predict(bt.mod, type="zero")*predict(bt.mod, type="response")
# predict for the missing spp
missing_burn$BurnTime<-predict(bt.mod, type="zero", newdata=missing_burn)*
  predict(bt.mod, type="response", newdata=missing_burn)

# now for ignitability
# model same as burn biomass - max = 11, min = 0
# dropped native as non sig
summary(ig.mod<-glm(cbind(round(Ignitability), round(11-Ignitability))~
                      logheight+logleaflength+logleafwidth+Regeneration+
                      Shade.Tolerance+Leaf.Form+Leaf.Longevity+Type+Woody+Simple,
                    data=traits2,family=binomial))
# model diagnostics 
anova(ig.mod, test="LRT")
plot(ig.mod)
DescTools::PseudoR2(ig.mod)#0.17 mcfadden - that's not bad

missing_burn$Ignitability<-predict.glm(ig.mod, type="response", newdata=missing_burn)*11

# finally, max temp
# think this is the only normal one - only issue is that massive over representation of 150deg - about 800 samples
# but i think it should still work in a normal glm?
# simple and native not sig
summary(mt.mod<-lm(MaxTemp~logheight+logleaflength+logleafwidth+Regeneration+Shade.Tolerance+
                      Leaf.Form+Leaf.Longevity+Type+Woody, data=traits2))
anova(mt.mod, test="LRT")
plot(mt.mod)
#0.22 r squared - pretty ok
missing_burn$MaxTemp<-predict(mt.mod, type="response", newdata=missing_burn)

# finally, add the missing_burn data to the burn data frame (need to merge it to get the nvs code and create the sample column etc)
rm(bb.mod, bt.mod, ig.mod, mt.mod)
missing_burn<-merge(missing_burn, nvs, by="SpeciesName", all.y=FALSE)
missing_burn$Sample<-"NA"
missing_burn$IgnitionTime<-"NA"
missing_burn<-missing_burn[,c(1,43,30,44,29,27,26,28,33)]
burn<-rbind(burn, missing_burn)
#write.csv(missing_burn,"../results/predicted_burndat.csv", row.names = F)
rm(missing_burn)

```

# Run PCA on flammability data, assign PC1 score to species as flammability score
```{r PCA on flammability}
# create mean value per species so each species has just one pca score
burn$logburntime<-log(burn$BurnTime+1)
burn$logburnbio<-log(burn$BurnBiomass+1)
pca_dat2<-burn[,c(5,8,10,11)]%>%aggregate(by=list(burn$NVSCode), FUN=mean, na.rm=T)
names(pca_dat2)<-c("NVSCode", "Combustibility", "Ignitability", "Sustainability", "Consumability")

burn.pca <- prcomp(pca_dat2[,c(2:5)], scale = TRUE) # perform a principal components analysis
summary(burn.pca)   # look at the variance explained
plot(burn.pca)      # plot the eigenvalues
biplot(burn.pca)    # plot the site scores and the species vectors

# assign PC scores to species
pca_dat2$PC1 <- burn.pca$x[,1] # extract the species scores and
pca_dat2$PC2 <- burn.pca$x[,2] # add them to the species summary dataset

# high PC1 = low flammability, invert so makes sense
pc1.inv<-pca_dat2$PC1+abs(min(pca_dat2$PC1)) #rescale so min=0
pc1.inv<-max(pc1.inv)-pc1.inv # invert
pca_dat2$model.flam<-pc1.inv

bbiplot<-autoplot(burn.pca, 	ellipse=F,loadings = TRUE, loadings.colour = 'black', loadings.label = TRUE, 
                  loadings.label.size = 4, loading.label.color = 'black',loadings.label.repel=T) 


bbiplot<-ggbiplot(burn.pca, obs.scale = 0.5, var.scale = 1)
plot<-arrangeGrob(plot2, bbiplot, nrow=1, ncol=2, widths=c(8,4))

ggsave(plot,file="../results/biplots.png", width=12, height=4, dpi=300)
rm(plot2, plot, bbiplot)
```

# Multiply community matrices by flammability score vector to get cwm of flammability
```{r community weighted flammability, echo=TRUE, results="hide"}
# remove all from species summary data that aren't in community
pca_dat3<-pca_dat2 %>% semi_join(community, by = "NVSCode")
#write.csv(pca_dat3, file="../results/final_species_flams.csv", row.names=F)

# make col 1 of community matrix into rownames so can multiply, create vector of flam traits (pc1)
rownames(cmat) <- cmat[,1]
cmat<-cmat[,c(2:ncol(cmat))]

traits<-as.data.frame(pca_dat3[,8])
names(traits)<-c("model.flam")
rownames(traits) <- pca_dat3[,1]

cwm_fd<-dbFD(traits,cmat)

aCWM<-cwm_fd$CWM

# reformatting on the cwm data frame
aCWM <-aCWM%>%
  tibble::rownames_to_column("PlotID")%>%
  dplyr::rename(Community_Flam = model.flam )

# add the veg data
aCWM<-community %>%
    dplyr::select(PlotID, GrahamClass) %>%
    distinct() %>%
    right_join(aCWM, by = 'PlotID')

aCWM$Farm<-stringr::word(aCWM$PlotID, 1)

aCWM<-subset(aCWM, Farm=="CAN") #select just canterbury as that's all we have the landscape for right now
# write data to csv - commented out to avoid overwriting
#write.csv(aCWM, file="../ls_model_inputs/community_flam.csv", row.names = F)

```

# Plot flammability by veg types on farms, export data for landscape analysis
```{r flammability plots by veg type}
a<-ggplot(aCWM, aes(GrahamClass, Community_Flam))+
  geom_boxplot()+
  theme(axis.text.x = element_text(angle=90))+
  xlab("")+
  ylab("Community Flammability Score")+
  facet_grid(.~Farm, scales="free")
a

ggsave(a, file="../results/community_flammability_vegtypes_graham_treefern.png", width=10, height=6, dpi=300)
```

This section estimates flammability for pine (continuous, diffuse and sparse) as no pine plots sampled in canterbury, and needed for the flammability scenarios. Based on assumption of monoculture of pinus radiata.
```{r pine flammability estimate}
# read in pine data and format NVS code species name as in other data frames
pine<-read.csv("../data/pine_IV.csv", header=T, stringsAsFactors = F)
pine$NVSCode<-pine$NVSCode%>%toupper()%>%tm::stripWhitespace()%>%trimws(.,"both")
pine$SpeciesName<-pine$SpeciesName%>%tm::stripWhitespace()%>%trimws(.,"both")

# make into matrix
temp.cmat2<-dcast(pine, formula=PlotID~NVSCode, value.var = "IV", sum)
# make col 1 of community matrix into rownames so can multiply, create vector of flam traits (pc1b)
cmat2<-as.matrix(temp.cmat2[,2])
rownames(cmat2) <- temp.cmat2[,1]
colnames(cmat2) <-"PINRAD"
rm(temp.cmat2)

temp.traits2<-as.data.frame(pca_dat2[,c(1,8)])
temp.traits2<-subset(temp.traits2, startsWith(temp.traits2$NVSCode, "PIN")==TRUE)
traits2<-as.data.frame(temp.traits2[,2])
colnames(traits2)<-"model.flam"
rownames(traits2) <- temp.traits2[,1]
rm(temp.traits2)


# need to do manually as won't work in FD with the dummy data
# multiply the IV values in community matrix by the mean pc1 score for pines
com2<-cmat2*mean(traits2$model.flam)

# calculate the sum of species IV in each site
av_com2 <- rowSums(cmat2, na.rm=F, dims=1)

#Then, we do the same with trait values:
av_com3 <- rowSums(com2, na.rm=F, dims=1)

#Finally, we divide the two previous matrix:
aCWM2 <-data.frame(av_com3/av_com2)%>%
  tibble::rownames_to_column("PlotID")%>%
  dplyr::rename(Community_Flam = av_com3.av_com2 )

# add the veg data
aCWM2<-pine %>%
    dplyr::select(PlotID, Veg_Class) %>%
    distinct() %>%
    right_join(aCWM2, by = 'PlotID')

# write data to csv - commented out to avoid overwriting
#write.csv(aCWM2, file="../ls_model_inputs/pine_community_flam.csv", row.names = F)
# tidy up
rm( pine, cmat2, com2, av_com3, av_com2)
```
