---
title: "prelim_veg_analysis"
author: "Jennifer Pannell"
date: "1 February 2019"
output: html_document
---

```{r setup}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
library(tidyr)
library(plyr)
```

## Read data, remove NA values

```{r veg data}
dat<-read.csv("cover_class_data_long_all.csv", header=T)
# get rid of the NA's
dat<-na.omit(dat)

# strip white space from species names
dat$SpeciesName<-trimws(dat$SpeciesName)
dat$PlotNo<-trimws(dat$PlotNo)

# create unique plot ID column
dat$ID<-paste(dat$Farm,dat$PlotNo)
# read in plot data & merge
plots<-read.csv("plot_info.csv", header=T)
plots$PlotNo<-trimws(plots$PlotNo)
dat<-merge(plots, dat, by="PlotNo")

```

## Divide into trees, shrubs, understorey
# Trees = above 2m
In each codeblock, aggregate trees, shrubs & understorey by farm & vegetation class, and by species, calcluating mean and SD and total cover abundance. 

```{r trees}
trees<-subset(dat, variable=="CoverClass.25m"|
                variable=="CoverClass12.25m"|
                variable=="CoverClass5.12m"|
                variable=="CoverClass2.5m")

# make into a summary table - one row per species per farm per habitat
summary.trees<-trees[,14]%>%aggregate(by=list(trees$FarmName, trees$VegClass, trees$SpeciesName), FUN=mean, na.rm=T)
names(summary.trees)<-c("FarmName", "VegClass", "SpeciesName", "MeanCover")
summary.trees$SDcover<-trees[,14]%>%aggregate(by=list(trees$FarmName, trees$VegClass, trees$SpeciesName), FUN=sd, na.rm=T)%>%.[,4]
summary.trees$SumCover<-trees[,14]%>%aggregate(by=list(trees$FarmName, trees$VegClass, trees$SpeciesName), FUN=sum, na.rm=T)%>%.[,4]
summary.trees<-trees%>%count(c("FarmName", "VegClass", "SpeciesName"))%>%merge(.,summary.trees, by=c("FarmName", "VegClass", "SpeciesName"))

summary.trees<-summary.trees[order(summary.trees$FarmName, summary.trees$VegClass, -summary.trees$SumCover),]
# add a "tree" column so can merge back later
summary.trees$Layer<-"tree"
```

# Shrubs = Shrubs = above 30cm
```{r shrubs}
shrubs<-subset(dat, variable=="CoverClass0.3.2m")

# make into a summary table - one row per species per farm
summary.shrubs<-shrubs[,14]%>%aggregate(by=list(shrubs$FarmName, shrubs$VegClass, shrubs$SpeciesName), FUN=mean, na.rm=T)
names(summary.shrubs)<-c("FarmName", "VegClass", "SpeciesName", "MeanCover")
summary.shrubs$SDcover<-shrubs[,14]%>%aggregate(by=list(shrubs$FarmName, shrubs$VegClass, shrubs$SpeciesName), FUN=sd, na.rm=T)%>%.[,4]
summary.shrubs$SumCover<-shrubs[,14]%>%aggregate(by=list(shrubs$FarmName, shrubs$VegClass, shrubs$SpeciesName), FUN=sum, na.rm=T)%>%.[,4]
summary.shrubs<-shrubs%>%count(c("FarmName", "VegClass", "SpeciesName"))%>%merge(.,summary.shrubs, by=c("FarmName", "VegClass", "SpeciesName"))

# add a "tree" column so can merge back later
summary.shrubs$Layer<-"shrub"
```

# Understorey = below 30cm
```{r understorey}
under<-subset(dat, variable=="CoverClass.0.3m")

# make into a summary table - one row per species per farm
summary.under<-under[,14]%>%aggregate(by=list(under$FarmName, under$VegClass, under$SpeciesName), FUN=mean, na.rm=T)
names(summary.under)<-c("FarmName","VegClass", "SpeciesName", "MeanCover")
summary.under$SDcover<-under[,14]%>%aggregate(by=list(under$FarmName, under$VegClass, under$SpeciesName), FUN=sd, na.rm=T)%>%.[,4]
summary.under$SumCover<-under[,14]%>%aggregate(by=list(under$FarmName, under$VegClass, under$SpeciesName), FUN=sum, na.rm=T)%>%.[,4]
summary.under<-under%>%count(c("FarmName","VegClass", "SpeciesName"))%>%merge(.,summary.under, by=c("FarmName","VegClass", "SpeciesName"))

# add a "tree" column so can merge back later
summary.under$Layer<-"understorey"
```

# Master data frame
Merge all of the understorey, shrub and tree dataframes back together to final data frame
```{r merge back}
summary<-rbind(summary.trees, summary.shrubs, summary.under)
# remove the extra data frames
rm(summary.shrubs, summary.trees, summary.under, shrubs, trees, under)

```

#Species lookup
Now merge with the NVS table to give us the scientific names of each species code
```{r merge scientific name from NVS}
names<-read.csv("CurrentNVSNames.csv", header=T)
summary$SpeciesName<-toupper(summary$SpeciesName)
names(summary)[3]<-"NVSCode"
names$NVSCode<-toupper(names$NVSCode)

summary<-merge(summary, names[,c(1,3,5,6)], by="NVSCode", all.x=TRUE)
summary<-summary[order(summary$FarmName, summary$Layer, summary$VegClass, -summary$SumCover),]
```

#Burn data
How many of theses species do we have flammability data for?
```{r merge burn data}
burn<-read.table("burn_list.txt", header=T, sep="\t")
congen<-read.table("congener_list.txt", header=T, sep="\t")

summary$burned<-summary$NVSCode%in%burn$NVSName
summary$congener<-summary$NVSCode%in%congen$NVSName

```

#Write summary file
```{r write file}
write.csv(summary, file="farm_summaries.csv", row.names = F)

```

