---
title: "Model Runs"
author: "Jennifer Pannell"
date: "25/09/2019"
output: html_document
---
## Introduction

This R markdown calls the final step of flammability analyses, the landscape community flammability models (file = landscape_model.R)
It requires community_flam.csv as an input, which is the output of community.Rmd
It also requires a csv of polygon IDs for the landscape with associated vegetation classes (polygons.csv), and a raster of polygon IDs (landscape_can.tif).
Finally, it either requires csvs of pasture and pine flammability estimates, or you will need to manually specify those values before running the "assign raster values" r chunk.

Note that Graham's landscape rasters have been aggregated by a factor of 4 to keep files manageable, and have been intersected with the LCDB to mask out areas of non vegetation.

```{r setup, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(raster)
library(grainscape)
library(spatialEco)
library(igraph)
```

Firstly, read in the data frames of community flammability and polygon IDs with their veg classes, as well as a raster with the polygon IDs.
```{r read in data}
#### read in data ####
# read in flammability data output from community.Rmd and rename GrahamClass to Veg_Class
sample.plots<-read.csv("../ls_model_inputs/community_flam.csv", header=T, stringsAsFactors = F)%>%dplyr::rename(Veg_Class=GrahamClass)
# read in table of polygon IDs and associated veg classes with which to assign flam values
polygons.raw<-read.csv("../ls_model_inputs//polygons.csv", header=T, stringsAsFactors = F)
# also read in raster of polygon IDs, use this to then reclassify as flam values
landscape<-raster("../ls_model_inputs//landscape_can.tif")
# read in pasture flammability estimate - if not using this, comment it out
# pasture<-read.csv("..//ls_model_inputs//pasture_community_flam.csv", header=T, stringsAsFactors = F)
# read in pine flammability estimates - if not using this, comment it out
pine<-read.csv("..//ls_model_inputs//pine_community_flam.csv", header=T, stringsAsFactors = F)
```

This section checks whether all of the woody veg classes in the landscape have been sampled
```{r missing value estimation}
# first, check that all of your landscape values that aren't pasture are represented by the plots
paste(unique(polygons.raw$Veg_Class), unique(polygons.raw$Veg_Class)%in%unique(sample.plots$Veg_Class))

# missing: 
# diffuse pine & kanuka & deciduous (note misspelling in original layer name)
# should be halfway between sparse and continuous of same classes
# mixed native sparse - minimum of other 2 mixed native classes
# continuous old growth & diffuse & sparse - assign mixed native respectively

# OK - so some are missing. Assign them as the mean in the next section
polygons.raw$sampled<-polygons.raw$Veg_Class%in%sample.plots$Veg_Class
summary(polygons.raw$sampled) # luckily it's quite a small proportion of the polygons

# assign values 
dec.diff<-(subset(sample.plots, Veg_Class=="Decidious (Contin.)")%>%.[,3]%>%mean()+
             subset(sample.plots, Veg_Class=="Decidious (Sparse)")%>%.[,3]%>%mean())/2
og.cont<-subset(sample.plots, Veg_Class=="Mixed Native (Contin.)")%>%.[,3]%>%mean()
og.diff<-subset(sample.plots, Veg_Class=="Mixed Native (Diffuse)")%>%.[,3]%>%mean()
og.spar<-subset(sample.plots, Veg_Class=="Mixed Native (Sparse)")%>%.[,3]%>%mean()

# assign pine values
pine.cont<-pine[pine$Veg_Class == "Pine (Contin.)", "Community_Flam"] 
pine.diff<-pine[pine$Veg_Class == "Pine (Diffuse)", "Community_Flam"] 
pine.spar<-pine[pine$Veg_Class == "Pine (Sparse)", "Community_Flam"] 
# also need to get the estimated community flammability for pasture. if using a generic low value, comment out
# pastureflam<-pasture$Community_Flam

# generic low value for pasture - needs to be lower than the minimum value so that all woody veg is more likely to 
# burn. If using the community flammability estimate instead, comment this out. 
pastureflam<-min(sample.plots$Community_Flam)/2

# also need a value for non veg - no flammability, but needs max resistance in next step. Have doubled the minimum
# value - needs to be distinctly different but still on same sort of scale. Doesn't matter actual value as will be 
# constant between the different scenarios.
nonveg<-min(sample.plots$Community_Flam)/4
```

This section determines the threshold for choosing what is a node of high flammability
```{r k means clustering}
# Get data into format that will be used in resistance surface - inverted 
km.dat<-max(sample.plots$Community_Flam)-sample.plots$Community_Flam # invert so it's resistance not flammability
hist(km.dat, breaks=20) # use histogram to decide on sensible number of clusters - 5 - v low, low, med, high, v high

# run k-means clustering wtih 5 classes
set.seed(20)
flamCluster <- kmeans(km.dat, 5, nstart = 20)
flamCluster

# plot outputs
sample.plots$cluster <- as.factor(flamCluster$cluster)
kmplot<-ggplot(sample.plots, aes(Veg_Class, km.dat, color = cluster)) + geom_point(size=3)+
  ylab("Plot Community Flammability")+
  scale_color_brewer(palette="Set1")+
  xlab("")+theme_bw()+theme(axis.text.x = element_text(angle=90))
#ggsave(kmplot, file="../results/kmeans_clusters.png", width=8, height=5)

# define resistance threshold below which patches should be "nodes" of high flammability 
# using k-means clustering - want all flam values in high or v high classes
# find cluster number of second-lowest mean ("high" class, remember they're inverted to correspond to resistance)
cluster.no<-which(flamCluster$centers==sort(flamCluster$centers)[2])
# set threshold as minimum resistance value (inverted flammability) that corresponds to that cluster
threshold<-subset(sample.plots, cluster==cluster.no)%>%.[,3]%>%min(.)
threshold<-max(sample.plots$Community_Flam)-threshold
```

```{r set params}
# specify how many bootstraps per scenario you want - recommend max 100
n<-100
# specify what proportion of the landscape you want to replant - set at 10% (0.1)
proportion.replant<-0.1
```
Each chunk takes approx 1 hour to run
```{r baseline scenario}
# set the input model data as the raw polygons data frame (not important here but important for next runs)
polygons<-polygons.raw
scenario<-"baseline"
source("landscape_model.R")
```

```{r pine scenario}
#reset polygons (removing the previous run data as has been saved already)
polygons<-polygons.raw
scenario<-"pine"
source("landscape_model.R")
```

```{r kanuka scenario}
polygons<-polygons.raw
scenario<-"kanuka"
source("landscape_model.R")
```

```{r native scenario}
polygons<-polygons.raw
scenario<-"native"
source("landscape_model.R")
```